\textbf{Response Letter}

### 2018-12-24 doc/aij18/major-revision/letter.tex
Updated 24 Dec 20.00

\textcolor[rgb]{1.00,0.00,0.50}{That depends on the domain we are trying to learn. Certainly, most planning domains do not need predicates with repeated variables, but in order to ensure the completeness of our learning approach we have opted to include it.}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ...  SE SIGUEN CUMPLIENDO LAS SYNTACTIC STRIPS CONSTRAINTS CON CONDITIONAL EFFECTS????? }}

@@

\textcolor[rgb]{1.00,0.00,0.50}{Removing symmetries would admittedly improve performance for heuristic planners. This removal can be achieved by ensuring the actions are programmed following some order, which can be done via some additional fluents. We think, however, that the compilation scheme should remain as simple and general as possible to facilitate its understanding.
}

\textcolor[rgb]{1.00,0.00,0.50}{Nevertheless, we want to thank the reviewer for the great idea and we will look into adding this optimization to the approach as a compilation option.}

@@

\textcolor{blue}{The positions of the validate actions among the apply actions is determined by the planner, which will verify that the state that results after the execution of an apply action comprises the observed state of the plan trace. We have added the following sentence in the document to clarify this point: "There will be a validate action in $\pi_\Lambda$ for every observed state in $\tau$. The position of the validate actions in $\pi_\Lambda$ will be determined by the planner checking that the state resulting after the execution of an apply action comprises the observed state $s_j\in\tau$."}

@@

\textcolor{blue}{With respect to the repetition of the definition of a \strips\ action model, conditional effects are introduced in section 4 because these are exclusively used for modeling the task that results from the compilation, $P_{\Lambda}=\langle F_{\Lambda},A_{\Lambda},I_{\Lambda},G_{\Lambda} \rangle$. Nevertheless, we have now incorporated the explanation about conditional effects within the section 4.2 'Compilation' since this is a merely syntactic aspect of the task formalization.}

@@

\textcolor{blue}{As indicated by the reviewer, timeouts are only observed in the setting with NO action sequences and NO state trajectories. We have added a few sentences providing more details on this issue.}

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{SOLO HE VISTO UNA FRASE DE TIMEOUTS SOBRE EL GRID ... Y EL RESTO DE DOMINIOS? NO SE PUEDE DECIR NADA???? }}

@@

@@

@@

\textcolor[rgb]{0.00,0.07,1.00}{In the remodeling of section 3, the paragraph about the size of the training dataset has been removed too. The ideas presented here have been moved to section 6.}

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ... NO HE VISTO ESTE PARRAFO EN LA SECCION 6, NO PUSISTE ESTA INFORMACION EN 6??}}

@@

\textcolor[rgb]{1.00,0.00,0.50}{The function $ar(\cdot)$ returns the arity of an action or predicate (the length of its argument list) and is first introduced in the Background section.}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ...}}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ...  SE PUEDE DECIR ALGO MAS O IGNORAMOS EL COMENTARIO?}}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ...  HE A—ADIDO ESTA FRASE EN EL TEXTO PERO SOLO CON RESPECTO AL GTM. MIRA A VER SI TE PARECE BIEN.}}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ...  HE A—ADIDO ALGO PARA CLARIFICAR ESTO EN EL TEXTO PERO NO SE SI EST¡ BIEN ... COMPROBAR}}

\textcolor{blue}{Hopefully the new section 3 (see main modification \#2) helps the reviewer clarify this question. }

@@

\subsection*{Reviewer \#3}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
First sentence of the Introduction: there is no satisfactory or generally accepted definition of "complete"ù domain model, given that a domain model is an abstraction of the domain being modelled. If the authors use such a term they should  make clear what their definition is. "Adequate"ùis a better word to use - in the sense of being adequate enough for use with a planner to solve a set of planning tasks.
\end{mdframed}

@@

@@

@@

\textcolor{blue}{We keep adding new domains as we work on the approach so that number is representative of how many domains we have tested our approach on. We did, however, leave one domain out, {\em Sokoban}. As a matter of fact, this domain has some of the features more difficult to handle for our approach, those are puzzle-like domains and domains with grid-like structure.}

@@

\textcolor{blue}{Predicates with arity 3 are certainly harder but still manageable. In order to proof this, we have added the {\em rovers} domain to the list of domains tested in section 6. }

>>>>

\textcolor{blue}{It depends on the domain we are trying to learn. Certainly, most planning domains do not need predicates with repeated variables, but in order to ensure the completeness of our learning approach we have opted to include it.}

@@

\textcolor{blue}{On the other hand, the assumptions regarding the syntactic \strips\ constraints still apply when using conditional effects}

@@

\textcolor{blue}{Removing symmetries would admittedly improve performance for heuristic planners. This removal can be achieved by ensuring the actions are programmed following some order, which can be done via some additional fluents. We think, however, that the compilation scheme should remain as simple and general as possible to facilitate its understanding.}

\textcolor{blue}{Nevertheless, we want to thank the reviewer for the great idea and we will look into adding this optimization to the approach as a compilation option.}

@@

\textcolor{blue}{The positions of the validate actions among the apply actions is determined by the planner, which will verify that the state that results after the execution of an apply action comprises the observed state of the plan trace. We have added the following sentence in the document to clarify this point: "There will be a validate action in $\pi_\Lambda$ for every observed state in $\tau$. The position of the validate actions in $\pi_\Lambda$ will be determined by the planner by checking that the state resulting after the execution of an apply action comprises the observed state $s_j\in\tau$."}

@@

\textcolor{blue}{With respect to the repetition of the definition of a \strips\ action model, conditional effects are introduced in section 4 because these are exclusively used for modeling the task that results from the compilation, $P_{\Lambda}=\langle F_{\Lambda},A_{\Lambda},I_{\Lambda},G_{\Lambda} \rangle$. We have now incorporated the explanation about conditional effects within the section 4.2 'Compilation' since this is a merely syntactic aspect of the task formalization.}

@@

\textcolor{blue}{Timeouts are only produced in the setting with NO action sequences and NO state trajectories. We have added some details on the domains where timeouts are found: in the grid domain when $|\mathcal{T}| = 3$, floortile when $|\mathcal{T}| = 4$ and four other domains. We refer the reviewer to the comment added in page 23 of section 6.2.}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{EVA ...}}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{SERGIO ...}}

@@

\textcolor[rgb]{0.00,0.07,1.00}{In the remodeling of section 3, the paragraph about the size of the training dataset has been removed as well. The ideas presented here have been moved to page 23, at the end of section 6.2.}

@@

\textcolor{blue}{The function $ar(\cdot)$ does not return a set, it returns the arity of an action or predicate; i.e., the length of its argument list. This is introduced in the Background section for the first time.}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{SERGIO ...}}

@@

\textcolor{blue}{The post-processing is applied to learning preconditions that are static literals and are never deleted or added. We inherit the same procedure for learning preconditions presented in [40]. The pseudo-code is presented in [40] (algorithm 2). }

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{PENDIENTE DIEGO MIRE UNA FRASE QUE LE HE MANDADO POR EMAIL}}

@@

@@

\textcolor{blue}{Yes, the reviewer is right in that we put it all in the planner and get the overall plan, both building actions and validating actions. What we mean by "solvable in two steps" is that a SAT-based planner internally solves the construction of the model in two \emph{time steps}: in one time step the truth value of all the model fluents that represent the preconditions is set, and in a second time step the value of all the model fluents that represent the effects is set. We have slightly modified the sentence to make it clear we refer to the SAT solving process of Madagascar.}

@@

%#########################################
\subsection*{Reviewer \#3}
%#########################################

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
First sentence of the Introduction: there is no satisfactory or generally accepted definition of "complete" domain model, given that a domain model is an abstraction of the domain being modelled. If the authors use such a term they should  make clear what their definition is. "Adequate" is a better word to use - in the sense of being adequate enough for use with a planner to solve a set of planning tasks.
\end{mdframed}

@@

\textcolor{blue}{We have substantially changed the explanation of the compilation scheme. We refer the reviewer to the main modification \#3. Besides an introductory paragraph that provides an overview of the compilation, we have included examples throughout the text to clarify the role of the insert actions, the apply actions and the validate actions. We have also renamed some concepts with more illustrative names.}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{PENDIENTE  .... y hay que revisar resultados, alguna cosa no cuadra ... }}

@@

\textcolor{blue}{We keep adding new domains as we work on the approach so this number is representative of how many domains we have tested our approach on. We did, however, leave one domain out, {\em Sokoban}. As a matter of fact, this domain presents some of the most difficult features to be able to be handled by our approach, particularly features intrinsic in puzzle-like domains and domains with grid-like structure. We have though included one more domain, the {\em rovers} domain.}

@@

\textcolor{blue}{Predicates with arity 3 are certainly harder but still manageable. In order to prove this, we have added the {\em rovers} domain to the list of domains tested in section 6. }
